\documentclass{article}[11pt]
%\usepackage[letterpaper,hmargin=1in,vmargin=1in]{geometry}
\usepackage[top=1in,bottom=.25in,, left=1in, right=1in]{geometry}
\usepackage{amssymb,amsmath,latexsym,url,amsfonts,xspace,multicol}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{anyfontsize}
\usepackage{tikz}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage{sectsty}
\usepackage{hyperref}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0.5ex}{0.5ex}
\titlespacing*{\subsection}{0pt}{0.5ex}{0.5ex}
\titlespacing*{\subsubsection}{0pt}{0.5ex}{0.5ex}

\usepackage[scaled]{helvet}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\normalfont
\newcommand{\mytab}[1]{\hspace{.2\textwidth}\rlap{#1}}
\newcommand{\myskip}{\vskip0.5in}

\thispagestyle{empty}
\definecolor{willblue}{HTML}{0000FF}
\definecolor{willgreen}{HTML}{FF00FF}
\sectionfont{\color{willblue}\Large}
\subsectionfont{\color{willgreen}\large}
\begin{document}

%\initpaper
%Hey
\setlength{\parskip}{0pt}


\begin{multicols}{2}
	{\section*{\Huge{William Harrison}}}
	\columnbreak
	\begin{flushleft}
		Phone: 612-360-0256 \\
		Email: harr9203@stthomas.edu \\
		Address: 1984 Grand Ave Apt 8, St. Paul, MN 55105
	\end{flushleft}
\end{multicols}
\begin{multicols}{2}
	\section*{Education}
	\subsection*{University of St. Thomas}
	Fall 2011 - Spring 2015 (expected)\\\\
	\begin{tabular}{@{}p{1.5cm}l}
	\textbf{Majors}		& Computer Science Information Security\\
				& Catholic Studies\\\\
	\end{tabular}
	\noindent
	\begin{tabular}{@{}p{1.5cm}l}
	\noindent\textbf{Courses}	& Algorithms, Information Security, \\
				& Object Oriented Design, Networking, \\
				& Modern Crytography, System Design. \\
	\end{tabular}
		\vfill
		\columnbreak
	\section*{Skills/Languages}
	\begin{tabular}{@{}p{2cm}l}
	Languages	& Python, Bash, HTML, CSS, Javascript, \\ 
			& Java, C, C++. \\\\\\
	Technologies	& Latex, vim, Wireshark, git, shell, Linux \\
			& Openssl, iOS, Android. \\
	\end{tabular}
		\vfill
		\columnbreak
\end{multicols}
	\section*{Work Experience}
	\subsection*{Medtronic}
	\begin{tabular}{@{}p{5cm}l}
		\textbf{Summer Engineering Associate} 	& \textbullet\ Maintained and updated in house website.\\
	Summer 2012 			& \textbullet\ Maintained a list of candidates for gaining special certification. \\
	Fall 2012 - Spring 2013 	& \textbullet\ Distributed instructional guides to help install statistical software. \\
	Summer 2013 			& \\
	Fall 2013 - Spring 2014	&
	\end{tabular}
	\hfill
	\subsection*{Wayzata Youth Hockey Association}
	\begin{tabular}{@{}p{5cm}l}
		\textbf{Peewee AA Coach} 		& \textbullet\ Helped run practices for elite 13-14 year old travel ice hockey team. \\
	2012 - 2013 	& \textbullet\ In charge of coaching by myself, groups of kids in rotation. \\
	2013 - 2014 	& \textbullet\ Main source of communication with parents about team related information.
	\end{tabular}
	\subsection*{App Development}
	\begin{tabular}{@{}p{5cm}l}
		\textbf{Independent App Developer}	& \textbullet\ Released app called The Catholic App: Find a Church near you. \\
	May 2009 -- August 2009 	& \textbullet\ Learned process of submitting apps on iOS and Android stores.
	\end{tabular}
\begin{multicols}{2}
	\section*{Projects}
		\subsection*{Quorridor Pathfinding}
		Built a tool for this game in Python to find the best path around placed walls to a winning destination. \href{https://github.com/bizzk3t/Graph}{Github}
		\subsection*{Latex MLA Autoformat Tool}
		Implemented a program to autoformat MLA citation standards used for my humanities papers. \href{https://github.com/bizzk3t/LatexMLA}{Github}
		\subsection*{Python Crytography}
		Built program in Python to test the strength of cryptographic functions for independent study in Modern Cryptography. \href{https://github.com/bizzk3t/PythonCrypto}{Github}
		\subsection*{Music Studio}
		Developed a framework and design for a unser music studio. Currently testing different ways to implement this program. The end product will be in C or C++.
	\subsection*{Chess}
		Developing a Role Playing Chess game that implements simple chess playing with a campaign that adds a unique experience.
		\vfill
		\columnbreak
	\section*{Interests}
	\subsection*{Ice Hockey}
	I played and now coach hockey. I love to incorporate the importance of life outside of hockey. I teach hockey as a game, but a game that can make you a complete person. 
	\subsection*{Music Production}
	I discoverd my interest in all music in college and decided to pay for piano lessons and watch videos about all apsects of music production. I never knew anything about it before and now I consider myself very proficient in that area.
	\subsection*{Arduino}
	Taught myself the basics of electrical engineering through experimentation with the Arduino. Implemented a simple dot matrix clock that displayed the time of day.
\end{multicols}
\begin{multicols}{2}
\end{multicols}

\end{document}







